Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species

### 2017-09-08 ms/RA/Wenk-RA-SI.Rnw
Update figures and MS for analysis on RA

\usepackage{suppmat}
\usepackage{listings}
\usepackage[T1]{fontenc} % Better underscores
\usepackage{longtable}
\usepackage{graphicx}

@@

\author{E. H. Wenk\textsuperscript{1,\textasteriskcentered}, K. Abramowicz\textsuperscript{2}, M. Westoby\textsuperscript{1}, D.S. Falster\textsuperscript{1} }
\affiliation{\textsuperscript{1} Biological Sciences, Macquarie University NSW 2109, Australia \\
\textsuperscript{2} Department of Mathematics and Mathematical Statistics, Ume{\aa} University, 90187 Ume{\aa}, Sweden \\
\textsuperscript{\textasteriskcentered} Correspondence author. E-mail: \email{ehwenk@gmail.com}
}

\usepackage[authoryear,sectionbib,sort]{natbib}
\bibliographystyle{amnat2}

@@

flowering_parts <- read.csv("Sup_Table_flowering_parts.csv", stringsAsFactors=FALSE, check.names=FALSE)
flowering_parts$Method <- clean_headers(flowering_parts$Method)
flowering_parts$Part <- firstup(flowering_parts$Part)
flowering_parts$Description <- firstup(flowering_parts$Description)

@@

\begingroup
\let\cleardoublepage\relax
\let\clearpage\relax
\tableofcontents
\endgroup

>>>>

\usepackage{float}
\usepackage{suppmat}
\usepackage{listings}
\usepackage[T1]{fontenc} % Better underscores
\usepackage{longtable}
\usepackage{graphicx}

@@

\author[a,*]{E.H. Wenk}
\author[b]{K. Abramowicz}
\author[a]{M. Westoby}
\author[c]{D.S. Falster}

\affil[a]{Department of Biological Sciences, Macquarie University NSW 2109, Australia}
\affil[b]{Department of Mathematics and Mathematical Statistics, Ume{\aa} University, 90187 Ume{\aa}, Sweden}
\affil[c]{Evolution and Ecology Research Centre, University of New South Wales, Australia}

%\textsuperscript{\textasteriskcentered} Correspondence author. E-mail: \email{ehwenk@gmail.com}

@@

flowering_parts <- read.csv("../Accessory/Sup_Table_flowering_parts.csv", stringsAsFactors=FALSE, check.names=FALSE)
flowering_parts$Method <- clean_headers(flowering_parts$Method)
flowering_parts$Part <- firstup(flowering_parts$Part)
flowering_parts$Description <- firstup(flowering_parts$Description)

@@
